An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-28 VLDB2026/main.tex
modify

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\
				Audio & 192 & 53,387 & 200 & 14& Audio \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
				Enron & 1369 & 94,987 & 200 & 23& Text \\
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\

>>>>

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\
				Audio & 192 & 53,387 & 200 & 14& Audio \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
				Enron & 1369 & 94,987 & 200 & 23& Text \\
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& \textcolor{red}{Text,Image} \\
